---
title: "Assisted Migration Model"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

#Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("print.matrix" = FALSE)
library(tidyverse)
library(spatstat.geom)
library(viridis)
library(rlang)
library(ggpubr)
library(foreach)
library(doParallel)
library(gganimate)
library(colorspace)
library(beepr)
library(av)
library(gifski)
library(magick)
library(gdata)
```

#Define Functions
functions for different stages of the model: death, mate choice, reproduction, dispersal, environmental change
```{r functions}


#Identify Phenotypes
#using rowSums may speed it up over apply but I'll come back to this point
#apermPOPS213 <- aperm(POPS, perm = c(2,1,3)) 
#POPS[,7,] <- rowSums(aperm(POPS[,10:29,], na.rm = TRUE)
phenotypes <- function(z){
  z[,7,] <-apply(z[,10:29,], MARGIN = c(1,3), sum)
  z[,8,] <- apply(z[,30:49,], MARGIN = c(1,3), sum)  
  return(z)
  }

#Mortality
death <- function(w){
  #Phenotypic mismatch
  #Site Means
  LANDarray <- simplify2array(apply(LAND, MARGIN = 1, FUN = function(x) matrix(data = x, ncol = 2, nrow = K, byrow = TRUE), simplify = FALSE))
  
  #Compute mortality probability
  mortprob <- 1-(exp(((-1)*(w[,7,]-LANDarray[,1,])^2)/Omega2grad)*exp(((-1)*(w[,8,]-LANDarray[,2,])^2)/Omega2env)*S0)
   #Compute mortality
  w[,9,] <- rbinom(n=K*Si, size=1, prob=mortprob)

  deathfun <- function(y) {
    y[which(y[,9]==1),]<-NA
    y<-y[order(y[,1]),]
    return(y)
  }
  w <- simplify2array(apply(w, MARGIN = 3, FUN = deathfun, simplify = FALSE))
  return(w)
}



#Mate Choice
#Mate choice is going to be a function we apply to a single population matrix, and then we are going to apply it across the third dimension of the array
matechoice <- function(v){
  
  #Reset several columns from last time
  v[,4:6] <- 0
  mfcount <- c(sum(v[,1]==0, na.rm = TRUE), sum(v[,1]==1, na.rm = TRUE))
  mincount <- min(mfcount, na.rm = TRUE)
  femalemin <- as.numeric(mfcount[1]<=mfcount[2])
  
  if(femalemin == 1) {
    matedfemaleindex <- which(v[,1]==0)
  }
  if(femalemin == 0) {
    matedfemaleindex <- sample(which(v[,1]==0), size = mincount, replace = FALSE)
  }
  maleindex <- which(v[,1]==1)
  v[matedfemaleindex,4]<-1
  v[matedfemaleindex,5] <- sample(maleindex, size = mincount, replace = FALSE)
  
  #Generate the offspring number per female
  v[which((v[,4]==1)&(v[,1]==0)), 6] <- rpois(sum(v[,4], na.rm = TRUE), lambda = MuOff)
  
  return(v)
}



#reproduction

#function used inside the reproducedisperse 
#Takes a vector of length two, and gives you a vector  of integers from the first integer to the second
#But doesn't allow it to be more than carrying capacity, since this is going to be used to index available spots for propagulues to land
#Also, when nobody is there and nobody lands there, then the result is c(1,0), which we should change to NA
funct <- function(r) { 
        if(r[1]>K) {
          return(NA)
        }
        else if (r[1]>r[2]) {
          return(NA)
        }
        else {
          
          return(r[1]:r[2])
          }
      }

#Includes reproduction, mutation, dispersal
#In this case, u has to be the full population array
reproducedisperse <- function(u) {
  
   #if no offspring, we can close out of this function, just return the same population array
  if(sum(u[,6,],na.rm = TRUE)==0) return(u)
  
  #Parents: female id, population, father, offspring #
  parents<- matrix(cbind(which(u[,6,]!=0, arr.ind = TRUE), u[,5,][which(u[,6,]!=0)], u[,6,][which(u[,6,]!=0)])[,c(2,1,3,4)],ncol = 4)
  #parents <- matrix(parents[which(parents[,4]>0),], ncol = 4)
  
  #identify offspring characteristics and parents
  #cols: source pop, target pop, then the same cols as u...sex, momID, dadID, ...
   offspring <- matrix(data = NA_real_, nrow = sum(u[,6,], na.rm = TRUE), ncol = 11+2*L)
  offspring[,c(1,4,5)] <- matrix(parents[,1:3],ncol = 3)[rep(seq_along(parents[,4]), parents[,4]),]
  #This randomizes the order of offspring
  offspring <- matrix(offspring[sample(nrow(offspring)),], ncol = 11+2*L)
  #identify target population (trying to identify movement first, so that I can take fewer samples of 1/-1, since it won't matter for the 90% that don't move)
  #identify differential
  offspring[,2] <- rgeom(n = nrow(offspring), prob = MuMovement)
  #how many move
  nmigrants <- length(which(offspring[,2]!=0))
  #if they move, figure out if it's up or down
  offspring[which(offspring[,2]!=0),2] <- offspring[which(offspring[,2]!=0),2]*sample(c(1,-1), size = nmigrants, replace = TRUE) + offspring[which(offspring[,2]!=0),1]
  #if they didn't move, set same as parent
  offspring[which(offspring[,2]==0),2] <- offspring[which(offspring[,2]==0),1]
  #Keep them within the boundaries
  offspring[which(offspring[,2]<1),2] <- 1
  offspring[which(offspring[,2]>Si),2] <- Si
  
  #number of offspring landing per site
  noffspring <- tabulate(offspring[,2], nbins = Si)
  
  #number of openings in each site
  openings <- which(is.na(u[,1,]), arr.ind = TRUE)
  nopenings <- tabulate(openings[,2], nbins = Si)
  
  #nopportunities = minimum of #openings/#offspring attempting to land there
  nopportunities <- pmin(nopenings, noffspring)
  
  #if nopportunities = 0 then all spots are full, return the same population array
  if(sum(nopportunities)==0) return(u)

  #how do we sample offspring so that we have only nopportunities in each deme
  #The offspring have previously been randomly sorted. Now we sort them by target deme
  offspring <- matrix(offspring[order(offspring[,2]),], ncol = 11+2*L)
  
  #set up retained matrix
  offspringretained <- matrix(NA, nrow = sum(nopportunities, na.rm = TRUE), ncol = 11+2*L)
    
    #This function retains only the number of offspring that there are room for
    groupsample <- function(s){
      return(matrix(offspring[which(offspring[,2]==s),],ncol=ncol(offspring))[sample(nrow(matrix(offspring[which(offspring[,2]==s),],ncol = ncol(offspring))),size = nopportunities[s], replace = FALSE),])
    }
    offspringretained <- do.call(rbind, simplify2array(sapply(as.list(1:Si),FUN = groupsample, simplify=TRUE)))
    
    
    #Now I will fill in the genotypes of the sampled individuals
    #set sex
    offspringretained[,3]<- rbinom(n = sum(nopportunities, na.rm = TRUE), size = 1, prob = 0.5)
    #set genotypes
    

      
      
      moms <- matrix(data = NA_real_, nrow = nrow(offspringretained), ncol = 2*L)
      dads <- matrix(data = NA_real_, nrow = nrow(offspringretained), ncol = 2*L)
      moms <- matrix(u[cbind(rep(offspringretained[,4], each = 2*L), 10:49, rep(offspringretained[,1], each = 2*L))], nrow = nrow(offspringretained), ncol = 2*L, byrow = TRUE)
      dads <- matrix(u[cbind(rep(offspringretained[,5], each = 2*L), 10:49, rep(offspringretained[,1], each = 2*L))], nrow = nrow(offspringretained), ncol = 2*L, byrow = TRUE)               
      
      #now fill in the offspring retained genotypes by sampling from the correct parent options
      #Mom's grad values coming from her mom or dad
      #Note: This will break down if we change L
      offspringretained[,12] <- moms[cbind(1:nrow(offspringretained), sample(c(01,11), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,13] <- moms[cbind(1:nrow(offspringretained), sample(c(02,12), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,14] <- moms[cbind(1:nrow(offspringretained), sample(c(03,13), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,15] <- moms[cbind(1:nrow(offspringretained), sample(c(04,14), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,16] <- moms[cbind(1:nrow(offspringretained), sample(c(05,15), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,17] <- moms[cbind(1:nrow(offspringretained), sample(c(06,16), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,18] <- moms[cbind(1:nrow(offspringretained), sample(c(07,17), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,19] <- moms[cbind(1:nrow(offspringretained), sample(c(08,18), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,20] <- moms[cbind(1:nrow(offspringretained), sample(c(09,19), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,21] <- moms[cbind(1:nrow(offspringretained), sample(c(10,20), size = nrow(offspringretained), replace = TRUE))]
      #Dad's grad values coming from his mom or dad
      offspringretained[,22] <- dads[cbind(1:nrow(offspringretained), sample(c(01,11), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,23] <- dads[cbind(1:nrow(offspringretained), sample(c(02,12), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,24] <- dads[cbind(1:nrow(offspringretained), sample(c(03,13), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,25] <- dads[cbind(1:nrow(offspringretained), sample(c(04,14), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,26] <- dads[cbind(1:nrow(offspringretained), sample(c(05,15), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,27] <- dads[cbind(1:nrow(offspringretained), sample(c(06,16), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,28] <- dads[cbind(1:nrow(offspringretained), sample(c(07,17), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,29] <- dads[cbind(1:nrow(offspringretained), sample(c(08,18), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,30] <- dads[cbind(1:nrow(offspringretained), sample(c(09,19), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,31] <- dads[cbind(1:nrow(offspringretained), sample(c(10,20), size = nrow(offspringretained), replace = TRUE))]
      #Mom's  Env value coming from her mom or dad
      offspringretained[,32] <- moms[cbind(1:nrow(offspringretained), sample(c(21,31), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,33] <- moms[cbind(1:nrow(offspringretained), sample(c(22,32), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,34] <- moms[cbind(1:nrow(offspringretained), sample(c(23,33), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,35] <- moms[cbind(1:nrow(offspringretained), sample(c(24,34), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,36] <- moms[cbind(1:nrow(offspringretained), sample(c(25,35), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,37] <- moms[cbind(1:nrow(offspringretained), sample(c(26,36), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,38] <- moms[cbind(1:nrow(offspringretained), sample(c(27,37), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,39] <- moms[cbind(1:nrow(offspringretained), sample(c(28,38), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,40] <- moms[cbind(1:nrow(offspringretained), sample(c(29,39), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,41] <- moms[cbind(1:nrow(offspringretained), sample(c(30,40), size = nrow(offspringretained), replace = TRUE))]
      #Dad's Env value coming from his mom or dad
      offspringretained[,42] <- dads[cbind(1:nrow(offspringretained), sample(c(21,31), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,43] <- dads[cbind(1:nrow(offspringretained), sample(c(22,32), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,44] <- dads[cbind(1:nrow(offspringretained), sample(c(23,33), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,45] <- dads[cbind(1:nrow(offspringretained), sample(c(24,34), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,46] <- dads[cbind(1:nrow(offspringretained), sample(c(25,35), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,47] <- dads[cbind(1:nrow(offspringretained), sample(c(26,36), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,48] <- dads[cbind(1:nrow(offspringretained), sample(c(27,37), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,49] <- dads[cbind(1:nrow(offspringretained), sample(c(28,38), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,50] <- dads[cbind(1:nrow(offspringretained), sample(c(29,39), size = nrow(offspringretained), replace = TRUE))]
      offspringretained[,51] <- dads[cbind(1:nrow(offspringretained), sample(c(30,40), size = nrow(offspringretained), replace = TRUE))]
 
      #Identify and add mutations
      mutations <- matrix(data = rbinom(n = 2*L*dim(offspringretained)[1], size = 1, prob = 0.001), ncol = 2*L)
      mutations[which(mutations==1)] <-rnorm(n = sum(mutations), mean = 0, sd = 0.0005)
      offspringretained[,12:(11+2*L)]<- offspringretained[,12:(11+2*L)]+mutations
      
      
      #This is the basis for how we'll call the empty spaces to put the offspring in 
      
      #this should be all the empty spots we need, and we will fill it with the values from offspringretained
     
      
      #calculate population size
      popsize <- colSums(!is.na(u[,1,]))
      
      

      
      #this should be all the empty spots we need, and we will fill it with the values from offspringretained
      rowsneeded <- unlist(apply(cbind(popsize+1, popsize+nopportunities), MARGIN = 1, FUN = funct, simplify = TRUE))
      rowsneeded <- rowsneeded[which(!is.na(rowsneeded))]
      u[cbind(rep(rowsneeded, each = dim(u)[2]), 1:dim(u)[2], rep(1:Si, times = nopportunities*dim(u)[2]))]<-as.vector(t(offspringretained[,3:(11+2*L)]))
      
return(u)
}

#The genetic rescue is implemented using two functions
#donorrecipients identifies and saves a list of donor-recipient populations pairs
#rescue moves individuals from donor to recipient populations

#Rescue a function that moves some individuals around
#inputs: p is the POPS population array
#strategy is the type of genetic rescue strategy to use, below are the 5 options
#None: no rescue
#Demographic:  rescue from the geographically closest single population
#Grad: rescue based on the closest population to the ending value of Grad
#GradEnv: rescue based on the closest population to the ending values of Grad and Env (bivariate distance)
#Multiple: rescue based on a mix of 5 local populations
#The last parameter is donrecplist: a 2d matrix with 2 columns. The first column is the IDs of donors, the second column is the IDs of recipients. The matrix will have 1 row per recipient population, unless strategy = "Multiple" then it will have (RescueSourceNumber x the number of recipient populations) rows.


donorrecipients <- function(q, strategy){
  if(strategy == "None") return(matrix(NA_integer_, ncol = 2))
  #Now identify populations in need
  #First sort the populations by size
  popsizes <- colSums(!is.na(q[,1,]))
  popsorted <- sort(popsizes, index.return = TRUE)
  #Identify the population size of the NumRescueSites smallest site
  popsortedmaxrecipient <- popsorted$x[NumRescueSites]
  #Identify all populations smaller than that threshold and a random selection of those equal to it (in case there are lots of ties, such as in the case where many local populations are extinct). I was worried about this case in particular, because taking just the 5 smallest if there are 25 pops at 0, then it will take the sites with the lowest index values, a bias we don't want to introduce here. Need to use resample to be robust to both ties and non-ties
  popsortedbelow <-popsorted$ix[which(popsorted$x<popsortedmaxrecipient)]
  popsortedequal <-popsorted$ix[which(popsorted$x==popsortedmaxrecipient)]
  recipients <- c(popsortedbelow, resample(x = popsortedequal, size = NumRescueSites-length(popsortedbelow)))

  #Set eligible donors
  
  #Sites for which there were offspring
  eligibledonors <- which(colSums(POPsim[,6,], na.rm = TRUE)!=0)
  #Site not already marked as recipients
  eligibledonors <- eligibledonors[which(!(eligibledonors %in% recipients))]
  
  #setup donor recipient matrix
  drmat <- matrix(NA_integer_, ncol = 2, nrow = length(recipients)) #this assumes 1 row per recipient, we'll resave the empty matrix if strategy = "multiple"
  drmat[,2] <- recipients
    if(strategy == "Demographic") {

      #Find all indices of eligible donors that equal the minimum distance, and randomly sample amongst them, such that there is no bias note, note that max.col could pick always the one to the north or south of the focal location if desired. There is no min.col, so we needed to use the max.col of the inverse to achieve the random tie breaking method
      drmat[,1] <- sapply(t(drmat[,2]), function(a, b) {b[max.col(matrix((1/abs(a-b)), nrow =1))]}, eligibledonors)
    } else if (strategy == "Grad") {
        drmat[,1] <- sapply(t(drmat[,2]), function(a, b,c, d) {b[max.col(matrix((1/abs(c$Grad[a]-d$Grad[b])), nrow =1))]}, b = eligibledonors, c = LANDfuture, d = LANDstarting)
    } else if (strategy == "GradEnv") {
        drmat[,1] <- sapply(t(drmat[,2]), function(a, b,c, d) {b[max.col(matrix(1/(as.matrix(dist(rbind(c[a,], d[b,])))[-1,1]), nrow = 1))]}, b = eligibledonors, c = LANDfuture, d = LANDstarting)
  }
  return(drmat)  
}

rescue <- function(p, donorcplist){
    #First, do each of the donor populations require all RescueSize individuals, or are there not enough spots?
  popsizes <- colSums(!is.na(p[,1,]))
  recipientpopsizes <- popsizes[donorcplist[,2]]
  recipientopportunities <- pmin(rep(RescueSize,NumRescueSites),(K-popsizes[donorcplist[,2]]))
  
  #If there are no spots to fill, we just skip to the end and return p
  if (sum(recipientopportunities, na.rm = TRUE) == 0) {
    
  } else {
  
  
  #Generate new offspring matrix
  offspringmoved <- matrix(NA, nrow = sum(recipientopportunities, na.rm = TRUE), ncol = 11+2*L)
  offspringmoved[,1] <- rep(donorcplist[,1], times = recipientopportunities)
  offspringmoved[,2] <- rep(donorcplist[,2], times = recipientopportunities)
  offspringmoved[,3] <- sample(c(0,1), size = nrow(offspringmoved), replace = TRUE)
  

  #Identify a random assortment of offspring to transplant with the same distribution of parents as those that naturally fell on the landscape
  #I'm not exactly taking the "excess" individuals, which would need to be more closely integrated into my reproducedisperse function

  for (transplant in 1:nrow(offspringmoved)){
    tempmoms <- p[,,offspringmoved[transplant,1]]
    tempmomsind <- which(tempmoms[,6]>0, arr.ind = TRUE)
    tempmomsweight <- tempmoms[tempmomsind,6]
    tempdads <- tempmoms[tempmomsind,5]
    tempparents <- cbind(tempmomsind, tempdads)
    offspringmoved[transplant,4:5] <- tempparents[sample(nrow(tempparents),size=1,replace=TRUE, prob = tempmomsweight),]
  }
  #Identify the parental genotypes
  momsmovers <- matrix(data = NA_real_, nrow = nrow(offspringmoved), ncol = 2*L)
      dadsmovers <- matrix(data = NA_real_, nrow = nrow(offspringmoved), ncol = 2*L)
      momsmovers <- matrix(p[cbind(rep(offspringmoved[,4], each = 2*L), 10:49, rep(offspringmoved[,1], each = 2*L))], nrow = nrow(offspringmoved), ncol = 2*L, byrow = TRUE)
      dadsmovers <- matrix(p[cbind(rep(offspringmoved[,5], each = 2*L), 10:49, rep(offspringmoved[,1], each = 2*L))], nrow = nrow(offspringmoved), ncol = 2*L, byrow = TRUE)     

  #now fill in the offspring moved genotypes by sampling from the correct parent options
      #Mom's grad values coming from her mom or dad
      #Note: This will break down if we change L
      offspringmoved[,12] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(01,11), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,13] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(02,12), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,14] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(03,13), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,15] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(04,14), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,16] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(05,15), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,17] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(06,16), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,18] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(07,17), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,19] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(08,18), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,20] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(09,19), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,21] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(10,20), size = nrow(offspringmoved), replace = TRUE))]
      #Dad's grad values coming from his mom or dad
      offspringmoved[,22] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(01,11), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,23] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(02,12), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,24] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(03,13), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,25] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(04,14), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,26] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(05,15), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,27] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(06,16), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,28] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(07,17), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,29] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(08,18), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,30] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(09,19), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,31] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(10,20), size = nrow(offspringmoved), replace = TRUE))]
      #Mom's  Env value coming from her mom or dad
      offspringmoved[,32] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(21,31), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,33] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(22,32), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,34] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(23,33), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,35] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(24,34), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,36] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(25,35), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,37] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(26,36), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,38] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(27,37), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,39] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(28,38), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,40] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(29,39), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,41] <- momsmovers[cbind(1:nrow(offspringmoved), sample(c(30,40), size = nrow(offspringmoved), replace = TRUE))]
      #Dad's Env value coming from his mom or dad
      offspringmoved[,42] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(21,31), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,43] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(22,32), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,44] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(23,33), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,45] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(24,34), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,46] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(25,35), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,47] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(26,36), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,48] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(27,37), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,49] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(28,38), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,50] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(29,39), size = nrow(offspringmoved), replace = TRUE))]
      offspringmoved[,51] <- dadsmovers[cbind(1:nrow(offspringmoved), sample(c(30,40), size = nrow(offspringmoved), replace = TRUE))]
 
  #Identify and add mutations to the movers
      mutationsmovers <- matrix(data = rbinom(n = 2*L*dim(offspringmoved)[1], size = 1, prob = 0.001), ncol = 2*L)
      mutationsmovers[which(mutationsmovers==1)] <-rnorm(n = sum(mutationsmovers), mean = 0, sd = 0.0005)
      offspringmoved[,12:(11+2*L)]<- offspringmoved[,12:(11+2*L)]+mutationsmovers
    #Now I'm going to fill in those transplanted individuals 
    
      rowsneededmove <- as.vector(unlist(apply(cbind(recipientpopsizes+1, recipientpopsizes+recipientopportunities), MARGIN = 1, FUN = funct, simplify = TRUE)))
      rowsneededmove <- rowsneededmove[which(!is.na(rowsneededmove))]
      p[cbind(rep(rowsneededmove, each = dim(p)[2]), 1:dim(p)[2], rep(donorcplist[,2], times = recipientopportunities*dim(p)[2]))]<-as.vector(t(offspringmoved[,3:(11+2*L)]))
    
       
      
    
}
      return(p)
}


#calculate population variance
popvar <- function(o){
  samplesize <- sum(!is.na(o))
  return(var(o, na.rm = TRUE)*(samplesize-1)/samplesize)
}

```


#Sensitivity Analysis 
Execute the simulation function over a range of values
For now, if I want to run a single simulation I'll just run this with one line
```{r Sensitivity}
#Set parameters that will be used the same in all simulations
#Landscape Parameters
Si <- 50 #Number of sites
K <- 500 #Carrying capacity in each site
L <- 20 #Total number of Locii

#Population growth/adaptation parameters
phenvar <- 0.3 #Starting variance for values of each allele
S0 <- 0.75 #Baseline survival rate, there will always be some mortality, even for the perfectly adapted
MuOff <- 3 #Mean offspring per female per reproductive event

#Simulation Length
timeperiod<- 600 

#Gradient Change parameters
#Note if deltaGradStart > timperiod, then there will be no gradient change
deltaGradStart <- 501 #Starting time point
deltaGradRate <- 0.05 #Change per time step
deltaGradLength <- 100 #Number of time steps

#Rescue parameters
#Note if RescueStart > timeperiod, then there will be no rescue
RescueStart <- 550 #Starting time point
RescueSites <- 0.1 #Proportion of sites to rescue (lowest RescueSites will be targeted for supplemental gene flow)
RescueSize <- 50 #Number of individual to send to each rescue site each year
RescueLength <- 1 #Number of time steps to repeat rescue over
NumRescueSites <- floor(Si*RescueSites) #Convert proportion of sites to a number, because I'll need to use that a lot

#Mode is the type of genetic rescue strategy to use, below are the 5 options
#None: no rescue
#Demographic:  rescue from the geographically closest single population
#Grad: rescue based on the closest population to the ending value of Grad
#GradEnv: rescue based on the closest population to the ending values of Grad and Env (bivariate distance)

#Multiple: rescue based on a mix of 5 local populations, not based on Grad or Env
RescueMode <- "Grad" 
RescueSourceNumber <- 5 #Number of sources to pull from if mode = "Multiple"

#Run ID for the sensitivity analysis. Usually I've been using a date
RunID <- "RescueTest2024_01_04Grad"

#Set values for parameters (migration, selection, environment type (fixed or variable))
MigSelvals <- data.frame(Mig = rep(c(0.9, 0.99, 0.999, 0.9999, 0.99999, 1),each = 20), Sel = rep(1:10,12), Envmode = c(rep("Fixed",10), rep("Variable",10)))


#Set up data collection
MigSel <-array(data = NA, dim = c(6,Si,dim(MigSelvals)[1]))
giflist <- vector(mode = "list", length = dim(MigSelvals)[1])


#How long does the loop take?
start_time <- Sys.time()
#The outer for-loop loops over different sets of parameter values, as established in MigSelvals
for (i in 1:dim(MigSelvals)[1]) {

  #Set temporary values of variables
  Omega2grad <- MigSelvals$Sel[i]
  Omega2env <- MigSelvals$Sel[i]
  MuMovement <- MigSelvals$Mig[i]
  EnvType <- MigSelvals$Envmode[i]
  
  #Setup landscape
  if (EnvType == "Variable") {
    LAND = data.frame(Grad = 1:Si, Env = sample(1:Si, replace = TRUE))
  } else if (EnvType == "Fixed") {
    LAND = data.frame(Grad = 1:Si, Env = as.integer(round(Si/2)))
  }
  #Save starting and future climate endpoint
  LANDstarting <- LAND
  LANDfuture <- LAND
  LANDfuture$Grad <- LAND$Grad + deltaGradRate*deltaGradLength
  
  #Initialize Population Array
#50 sheets for 50 sites
#First 9 columns: Sex, MomID, DadID, Mate, MateID, Offspring#, GradPhenotype, EnvPhenotype, Died?
#MomID and DadID can just be the row number, not an ID column that we keep track of because it will just be used to determine genotype during the reproduction phase, then the info can be lost/reset
#Mate Binary indicator, will they mate this time step (1) or not (0) 
# MateID will be the row number of the mate, not an ID column
#Offspring # will be reset each time step
#GradMismatch and EnvMismatch shows how far the individual is from the mean
#As will Died?
#then there will be 40 columns per individual representing 2 alleles each for each of 20 locii - 10 related to Env, 10 related to Grad, the first 10 are the Grad from mom, next 10 are the Grad from dad, next 10 are the Env from mom, next 10 are the Env from dad
  
  
  #Initialize Full population
  POPsim <- array(dim = c(K,9+2*L, Si))
  #We can set Female = 0, Male = 1
  POPsim[,1,] <- sample(c(0,1), Si*K, replace = TRUE)
  #Normal variation in genotype
  POPsim[,10:49,] <- rnorm(2*L*K*Si, 0, phenvar)
  #Add Grad Mean to first 20 
  POPsim[,10:29,] <- POPsim[,10:29,] + array(data = sort(rep(LAND$Grad/20, K*L)), dim = c(K, L, Si)) 
  #Add Env Means to second 20
  POPsim[,30:49,] <- POPsim[,30:49,] + array(data = as.vector(simplify2array(lapply(LAND$Env/20, rep, times = K*L), higher = TRUE)), dim = c(K, L, Si))

  #Identify Phenotypes
  POPsim[,7,] <-apply(POPsim[,10:29,], MARGIN = c(1,3), sum)
  POPsim[,8,] <- apply(POPsim[,30:49,], MARGIN = c(1,3), sum)  

  ###Set contents for data collection

  landgradovertime <- matrix(NA, nrow = timeperiod, ncol = Si)  
  landenvovertime <- matrix(NA, nrow = timeperiod, ncol = Si)
  popovertime <- matrix(NA, nrow = timeperiod, ncol = Si)
  Gradovertime <- matrix(NA, nrow = timeperiod, ncol = Si)
  Envovertime <- matrix(NA, nrow = timeperiod, ncol = Si)
  Gradvarovertime <- matrix(NA, nrow = timeperiod, ncol = Si)
  Envvarovertime <- matrix(NA, nrow = timeperiod, ncol = Si)

  
  #Simulate population and evolutionary dynamics with these parameters
  for(t in 1:timeperiod){
    #No environmental change except in this last else if statement
    if(t< deltaGradStart){
    } else if (t >= (deltaGradStart + deltaGradLength)){
    } else {LAND$Grad <- LAND$Grad + deltaGradRate}
    POPsim <- death(POPsim)
    POPsim <- simplify2array(apply(POPsim, MARGIN = 3, FUN = matechoice, simplify = FALSE))
    POPsim <- reproducedisperse(POPsim)
    POPsim <- phenotypes(POPsim)
    if(t == RescueStart) donorrecipientslist <- donorrecipients(POPsim, strategy = RescueMode)
    if((t == RescueStart) & (RescueMode != "None")) POPsim <- rescue(POPsim, donorcplist = donorrecipientslist)
    landgradovertime[t,] <- LAND$Grad
    landenvovertime[t,] <- LAND$Env
    popovertime[t,] <- colSums(!is.na(POPsim[,1,]))
    Gradovertime[t,] <- colSums(POPsim[,7,],na.rm = TRUE)/colSums(!is.na(POPsim[,7,]), na.rm = TRUE)-LAND$Grad
    Envovertime[t,] <- colSums(POPsim[,8,],na.rm = TRUE)/colSums(!is.na(POPsim[,8,]), na.rm = TRUE)-LAND$Env
    Gradvarovertime[t,] <- apply(POPsim[,7,], MARGIN = 2, FUN = popvar)
    Envvarovertime[t,] <- apply(POPsim[,8,], MARGIN = 2, FUN = popvar)
    #Cancel the remainder of the simulation if the entire metapopulation dies out
    if (sum(POPsim[,1,], na.rm = TRUE)==0) break
  }
  
  #Save Ending population information
  enddata <- matrix(NA, nrow = 6, ncol = Si)
  enddata[1,]<- colSums(!is.na(POPsim[,1,]))
  #Maladaptation
  enddata[2,] <- colSums(POPsim[,7,],na.rm = TRUE)/colSums(!is.na(POPsim[,7,]), na.rm = TRUE)-LAND$Grad
  enddata[3,] <- colSums(POPsim[,8,],na.rm = TRUE)/colSums(!is.na(POPsim[,8,]), na.rm = TRUE)-LAND$Env
  #Phenotypic variance
  #variance for gradient
  enddata[4,] <- apply(POPsim[,7,], MARGIN = 2, FUN = popvar)
  #variance for environment
  enddata[5,] <- apply(POPsim[,8,], MARGIN = 2, FUN = popvar)
  enddata[6,] <- t

  #Save full dataset
  landgradovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Land.Grad", Value = as.vector(landgradovertime))
  landenvovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Land.Env", Value = as.vector(landenvovertime))
  popovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Pop.Size", Value = as.vector(popovertime))
  gradovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Grad.Maladapt", Value = as.vector(Gradovertime))
  envovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Env.Maladapt", Value = as.vector(Envovertime))
  gradvarovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Grad.Var", Value = as.vector(Gradvarovertime))
  envvarovertimedf <- data.frame(Site = rep(1:Si, each = timeperiod), Time = rep(1:timeperiod, times = Si), Variable = "Env.Var", Value = as.vector(Envvarovertime))
  dataovertimedf <- rbind(landgradovertimedf, landenvovertimedf, popovertimedf, gradovertimedf, envovertimedf, gradvarovertimedf, envvarovertimedf)
  #This last filter cuts the dataset off when the population goes extinct, that way the 

  
  #Save information into big dataset before next step
  MigSel[,,i] <- enddata
  giflist[[i]] <- filter(dataovertimedf, Time <= mean(MigSel[6,,i], na.rm = TRUE))
  #Update Counter
  print(paste("Step",i,"out of",dim(MigSelvals)[1],Sys.time()))
} 
end_time <- Sys.time()
end_time - start_time
save(MigSelvals, MigSel, giflist, donorrecipientslist, file = paste0("Outputs/Sensitivity/", RunID, ".Rdata"))

```

Simple Plots of the endpoint of each simulation
```{r simplesensitivityplots}
  means <- apply(MigSel, MARGIN = c(1,3), FUN = mean, na.rm = TRUE)
  popmeans <- means[1,]
  gradmeans <- means[2,]
  envmeans <- means[3,]
  gradvars <- means[4,]
  envvars <- means[5,]
  plotdatadf <- data.frame(Mig = MigSelvals$Mig, Sel = MigSelvals$Sel, Envmode = MigSelvals$Envmode, popmeans, gradmeans, envmeans, gradvars, envvars)

popmeansfixed <- ggplot(data = filter(plotdatadf, Envmode == "Fixed"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = popmeans)) + scale_fill_viridis(limits = c(0,500)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

popmeansvariable <- ggplot(data = filter(plotdatadf, Envmode == "Variable"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = popmeans)) + scale_fill_viridis(limits = c(0,500)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

gradmeansfixed <- ggplot(data = filter(plotdatadf, Envmode == "Fixed"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = gradmeans)) + scale_fill_continuous_divergingx(palette = 'RdBu', limits = c(-2.2, 2.2)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()
  
gradmeansvariable <- ggplot(data = filter(plotdatadf, Envmode == "Variable"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = gradmeans)) + scale_fill_continuous_divergingx(palette = 'RdBu', limits = c(-2.2, 2.2)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

envmeansfixed <- ggplot(data = filter(plotdatadf, Envmode == "Fixed"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = envmeans)) + scale_fill_continuous_divergingx(palette = 'RdBu', limits = c(-3.2, 5.4)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

envmeansvariable <- ggplot(data = filter(plotdatadf, Envmode == "Variable"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = envmeans)) + scale_fill_continuous_divergingx(palette = 'RdBu', limits = c(-3.2, 5.4)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

gradvarsfixed <- ggplot(data = filter(plotdatadf, Envmode == "Fixed"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = gradvars)) + scale_fill_viridis(limits = c(0,0.5)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

gradvarsvariable <- ggplot(data = filter(plotdatadf, Envmode == "Variable"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = gradvars)) + scale_fill_viridis(limits = c(0,0.5)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

envvarsfixed <- ggplot(data = filter(plotdatadf, Envmode == "Fixed"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = envvars)) + scale_fill_viridis(limits = c(0,42)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()

envvarsvariable <- ggplot(data = filter(plotdatadf, Envmode == "Variable"), aes(x = (1.000001-Mig), y = (11-Sel))) + geom_raster(aes(fill = envvars)) + scale_fill_viridis(limits = c(0,42)) + scale_x_continuous(breaks = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01"), trans = "log10") + xlab("Proportion Migrants") + ylab("Selection Strength") + theme_classic()


endpointsplot <- ggpubr:::ggarrange(plotlist = list(popmeansfixed, popmeansvariable, gradmeansfixed, gradmeansvariable, envmeansfixed, envmeansvariable, gradvarsfixed, gradvarsvariable, envvarsfixed, envvarsvariable), ncol = 2, nrow = 5)

pdf(file = paste0("Outputs/Sensitivity/",RunID,"_EndPoint_Plots.pdf"))
endpointsplot
dev.off()
```

Time series plots of each population over time
```{r }

```

#Sensitivity Plots
Animations of of every simulation in MigSelVals
```{r sensitivyanalysisgifs}
gif_list_animated <- vector(mode = "list", length = dim(MigSelvals)[1])
mp4_list_animated <- vector(mode = "list", length = dim(MigSelvals)[1])

start_time <- Sys.time()
for (j in 116:dim(MigSelvals)[1]){
  
  templandgrad <- ggplot(data = filter(giflist[[j]], Variable == "Land.Grad"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_viridis(limits = c(0,(Si+(deltaGradRate*deltaGradLength))), option = "G") +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
  templandgradgif <- image_read(animate(templandgrad, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))

  templandenv <- ggplot(data = filter(giflist[[j]], Variable == "Land.Env"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_viridis(limits = c(0,Si), option = "G") +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
  templandenvgif <- image_read(animate(templandenv, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))

  temppop <- ggplot(data = filter(giflist[[j]], Variable == "Pop.Size"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_viridis(limits = c(0,K), option = "D") +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
temppopgif <- image_read(animate(temppop, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))

  tempgrad <- ggplot(data = filter(giflist[[j]], Variable == "Grad.Maladapt"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_continuous_divergingx(palette = 'RdBu') +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
tempgradgif <- image_read(animate(tempgrad, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))

  tempenv <- ggplot(data = filter(giflist[[j]], Variable == "Env.Maladapt"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_continuous_divergingx(palette = 'RdBu') +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
tempenvgif <- image_read(animate(tempenv, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))

  tempgradvar <- ggplot(data = filter(giflist[[j]], Variable == "Grad.Var"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_viridis(option = "B") +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
tempgradvargif <- image_read(animate(tempgradvar, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))
 
  tempenvvar <- ggplot(data = filter(giflist[[j]], Variable == "Env.Var"), aes(x = Variable, y = Site)) + geom_raster(aes(fill = Value)) + scale_y_continuous(breaks = c(1, seq(from = 10, to = Si, by = 10))) + scale_fill_viridis(option = "B") +  xlab(NULL) + theme_classic() + theme(legend.position = "top", axis.line.x = element_blank(), axis.ticks.x = element_blank()) + labs(title = "{closest_state}") + transition_states(Time)
tempenvvargif <- image_read(animate(tempenvvar, nframes = mean(MigSel[6,,j], na.rm = TRUE), width = 200))


  tempnewgif <- image_append(c(temppopgif[1], templandgradgif[1], tempgradgif[1], tempgradvargif[1], templandenvgif[1], tempenvgif[1], tempenvvargif[1]))
  for(k in 2:mean(MigSel[6,,j], na.rm = TRUE)){
    tempcombined <- image_append(c(temppopgif[k], templandgradgif[k], tempgradgif[k], tempgradvargif[k], templandenvgif[k], tempenvgif[k], tempenvvargif[k]))
    tempnewgif <- c(tempnewgif, tempcombined)
  }
  gif_list_animated[[j]] <- tempnewgif
  image_write_gif(tempnewgif, path = paste0("Outputs/Sensitivity/GIFs/",RunID,"Mig", MigSelvals[j,1],"Sel", MigSelvals[j,2],MigSelvals[j,3],".gif"))

  temp_new_mp4 <- image_convert(tempnewgif, "mp4")
  temp_new_mp4%>%image_write_video(path = paste0("Outputs/Sensitivity/mp4s/",RunID,"Mig", MigSelvals[j,1],"Sel", MigSelvals[j,2],MigSelvals[j,3],".mp4"))
  mp4_list_animated[[j]] <- temp_new_mp4
  
  print(paste("Animating Step",j,"out of",length(gif_list_animated),Sys.time()))
  }
save(gif_list_animated, mp4_list_animated, file = paste0("Outputs/Sensitivity/", RunID, "Animations.Rdata"))
end_time <- Sys.time()
end_time - start_time



```

