---
title: "Assisted Migration Model"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

#Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("print.matrix" = FALSE)
library(tidyverse)
library(spatstat.geom)
```

#Define Constants
```{r constants}
Si <- 50 #Number of sites
K <- 100 #Carrying capacity in each site
L <- 20 #Total number of Locii

Mu0 <- 0.1 #Baseline mortality
```

#Landscape
```{r landscape}


LAND = data.frame(Grad = 1:Si, Env = sample(1:Si, replace = TRUE))
plot(Env~Grad, data = LAND)


```

#Generate Populations
```{r pops}

#Initialize Population Array
#50 sheets for 50 sites
#First 9 columns: Sex, MomID, DadID, Mate, MateID, Offspring#, GradMismatch, EnvMismatch, Died?
#MomID and DadID can just be the row number, not an ID column that we keep track of because it will just be used to determine genotype during the reproduction phase, then the info can be lost/reset
#Mate Binary indicator, will they mate this time step (1) or not (0) 
# MateID will be the row number of the mate, not an ID column
#Offspring # will be reset each time step
#GradMismatch and EnvMismatch shows how far the individual is from the mean
#As will Died?
#then there will be 40 columns per individual representing 2 alleles each for each of 20 locii - 10 related to Env, 10 related to Grad, the first 10 are the Grad from mom, next 10 are the Grad from dad, next 10 are the Env from mom, next 10 are the Env from dad

#Initialize Full population
POPS <- array(dim = c(K,11+2*L, Si))
#We can set Female = 0, Male = 1
POPS[,1,] <- sample(c(0,1), Si*K, replace = TRUE)
#Normal variation in genotype
POPS[,10:49,] <- rnorm(2*L*K*Si, 0, 0.03)
#Add Grad Mean to first 20 
POPS[,10:29,] <- POPS[,10:29,] + array(data = sort(rep(LAND$Grad/20, K*L)), dim = c(K, L, Si)) 
#Add Env Means to second 20
POPS[,30:49,] <- POPS[,30:49,] + array(data = as.vector(simplify2array(lapply(LAND$Env/20, rep, times = 100*L), higher = TRUE)), dim = c(K, L, Si))
#POPS[,50,] is going to be dispersal [,51] is going to be dispersaltarget
#Give Phenotypes
POPS[,7,] <-apply(POPS[,10:29,], MARGIN = c(1,3), sum)

#using rowSums may speed it up over apply but I'll come. ack to this point
#apermPOPS213 <- aperm(POPS, perm = c(2,1,3)) 
#POPS[,7,] <- rowSums(aperm(POPS[,10:29,], na.rm = TRUE)
POPS[,8,] <- apply(POPS[,30:49,], MARGIN = c(1,3), sum)  

  

```

#Define Functions
functions for different stages of the model: death, mate choice, reproduction, dispersal, environmental change
```{r functions}


#Mortality
death <- function(POPS){
  #Phenotypic mismatch
  #Site Means
  LANDarray <- simplify2array(apply(LAND, MARGIN = 1, FUN = function(x) matrix(data = x, ncol = 2, nrow = 100, byrow = TRUE), simplify = FALSE))
  #2D euclidean distance
  Dist <- sqrt((POPS[,7,]-LANDarray[,1,])^2+(POPS[,8,]-LANDarray[,2,])^2)
  #Set probability of surviving this time-step proportional to Dist + some baseline mortality
  POPS[,9,] <- rbinom(5000,1,Dist+Mu0)
  deathfun <- function(x) {
    x[which(x[,9]==1),]<-NA
    return(x)
  }
  POPS <- simplify2array(apply(POPS, MARGIN = 3, FUN = deathfun, simplify = FALSE))
  return(POPS)
}

POPS <- death(POPS)


#Mate Choice
#Mate choice is going to be a function we apply to a single population matrix, and then we are going to apply it across the third dimension of the array
matechoice <- function(x){
  
  mfcount <- c(sum(x[,1]==0, na.rm = TRUE), sum(x[,1]==1, na.rm = TRUE))
  mincount <- min(mfcount, na.rm = TRUE)
  femalemin <- as.numeric(mfcount[1]<=mfcount[2])
  
  if(femalemin == 1) {
    matedfemaleindex <- which(x[,1]==0)
  }
  if(femalemin == 0) {
    matedfemaleindex <- sample(which(x[,1]==0), size = mincount, replace = FALSE)
  }
  maleindex <- which(x[,1]==1)
  x[matedfemaleindex,4]<-1
  x[matedfemaleindex,5] <- sample(maleindex, size = mincount, replace = FALSE)
  
  #Generate the offspring number per female
  x[which((x[,4]==1)&(x[,1]==0)), 6] <- rpois(sum(x[,4], na.rm = TRUE), lambda = 2)
  
  return(x)
}

POPS <- simplify2array(apply(POPS, MARGIN = 3, FUN = matechoice, simplify = FALSE))

#reproduction
#I'll structure this like mate choice, as a process to happen to a 2d population matrix, and then I'll apply it along the third axis of the array
reproducedisperse <- function(x) {
  
  offspring <- matrix(data = NA, nrow = )
  
  
  #Generate the offspring number per female
  x[which((x[,4]==1)&(x[,1]==0)), 6] <- rpois(sum(x[,4], na.rm = TRUE), lambda = 2)

  #all available rows
  availableindex <- which(is.na(x[,1]))
  #take the minimum length of all available rows, or the total number of offspring produced
  availableindex <- availableindex[1:min(length(availableindex), sum(x[,6], na.rm = TRUE))]
  #Randomly assign gender
  x[availableindex, 1] <- sample(c(0,1), size = length(availableindex), replace = TRUE)
  #Identify mothers
  x[availableindex,2] <- sample(rep(which(x[,4]==1),x[which(x[,4]==1),6]), size = length(availableindex), replace = FALSE)
  #Identify matched fathers
  x[availableindex,3] <- x[x[availableindex,2],5]
  
  #Sample new genotypes, take one of mom's alleles
  
  x[availableindex,10] <- apply(x[x[availableindex,2],c(10,20)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,11] <- apply(x[x[availableindex,2],c(11,21)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,12] <- apply(x[x[availableindex,2],c(12,22)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,13] <- apply(x[x[availableindex,2],c(13,23)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,14] <- apply(x[x[availableindex,2],c(14,24)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,15] <- apply(x[x[availableindex,2],c(15,25)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,16] <- apply(x[x[availableindex,2],c(16,26)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,17] <- apply(x[x[availableindex,2],c(17,27)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,18] <- apply(x[x[availableindex,2],c(18,28)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,19] <- apply(x[x[availableindex,2],c(19,29)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,30] <- apply(x[x[availableindex,2],c(30,40)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,31] <- apply(x[x[availableindex,2],c(31,41)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,32] <- apply(x[x[availableindex,2],c(32,42)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,33] <- apply(x[x[availableindex,2],c(33,43)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,34] <- apply(x[x[availableindex,2],c(30,44)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,35] <- apply(x[x[availableindex,2],c(31,45)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,36] <- apply(x[x[availableindex,2],c(32,46)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,37] <- apply(x[x[availableindex,2],c(33,47)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,38] <- apply(x[x[availableindex,2],c(30,48)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,39] <- apply(x[x[availableindex,2],c(31,49)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  
  #and one of dad's
  x[availableindex,20] <- apply(x[x[availableindex,3],c(10,20)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,21] <- apply(x[x[availableindex,3],c(11,21)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,22] <- apply(x[x[availableindex,3],c(12,22)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,23] <- apply(x[x[availableindex,3],c(13,23)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,24] <- apply(x[x[availableindex,3],c(14,24)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,25] <- apply(x[x[availableindex,3],c(15,25)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,26] <- apply(x[x[availableindex,3],c(16,26)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,27] <- apply(x[x[availableindex,3],c(17,27)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,28] <- apply(x[x[availableindex,3],c(18,28)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,29] <- apply(x[x[availableindex,3],c(19,29)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,40] <- apply(x[x[availableindex,3],c(30,40)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,41] <- apply(x[x[availableindex,3],c(31,41)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,42] <- apply(x[x[availableindex,3],c(32,42)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,43] <- apply(x[x[availableindex,3],c(33,43)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,44] <- apply(x[x[availableindex,3],c(30,44)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,45] <- apply(x[x[availableindex,3],c(31,45)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,46] <- apply(x[x[availableindex,3],c(32,46)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,47] <- apply(x[x[availableindex,3],c(33,47)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,48] <- apply(x[x[availableindex,3],c(30,48)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  x[availableindex,49] <- apply(x[x[availableindex,3],c(31,49)], MARGIN = 1, sample, size = 1, simplify = TRUE)
  
  #Potentially need to add some mutations at this step
    return(x)

}

POPS <- simplify2array(apply(POPS, MARGIN = 3, FUN = reproduce, simplify = FALSE))

dispersal <- function(x){
  x[which]
  
  
  x[which(!(is.na(x[1,,])),arr.ind=TRUE)[,1],50,which(!(is.na(x[1,,])),arr.ind=TRUE)[,2]] <- rbinom(n = length(which(!is.na(POPS[1,,]))), size = 1, prob = 0.01)
  x[which(!(is.na(x[1,,]))),51,] <- sample(c(1,-1), size = 1, )*sample(c(1,2,3), replace = TRUE, prob = c(0.9,0.09,0.01))
  return(x)
  }


POPS2 <- dispersal(POPS)


```

#Simulation
```{r simulation}

start_time <- Sys.time()
ts <- 20
for(i in 1:ts){
  POPS<- death(POPS)
  POPS <- simplify2array(apply(POPS, MARGIN = 3, FUN = matechoice, simplify = FALSE))
  POPS <- simplify2array(apply(POPS, MARGIN = 3, FUN = reproduce, simplify = FALSE))
  }
end_time <- Sys.time()
end_time - start_time


ts         <- 0;
time_steps <- 20;
POPS_hist  <- NULL; # Here's the list
while(ts < time_steps){
    POPS            <- movement(POPS)
    ts              <- ts + 1
    POPS_hist[[ts]] <- POPS; # Add to list
}
print(POPS);
