---
title: "DataCleaning_Rescue"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

Process Remaining Rescue-Scenario Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(viridis)
library(ggpubr)
library(colorspace)
library(grid)
library(gdata)
library(str2str)
library(parallel)
library(beepr)

```


```{r loaddata}
load("loadedFullList.Rdata")
```

There are 3 types of comparisons worth making:
1. Comparing the average of all sites on the landscape between no rescue and rescue - did the effect percolate up to the whole metapopulation
2. Comparing the (5) demes with the smallest nonzero population size between no rescue and rescue - did the effect the most marginal demes in the metapopulation
3. Comparing the (5) demes that received supplementation between no rescue and rescue - did the target demes benefit? 

So far this only implements #1

```{r functions}
#Find the data at time point 499, just before rescue occurs
prerescuedatasubset <- function(x){
  filter(x[[1]], Time == 499)
}

```

```{r cleanrescuedata}

#format grad and env match then pivot everything so that we have differentials between each type of rescue and the no-rescue scenario


convert_to_number <- function(dataframe){
  dataframe[["Value"]] <- as.numeric(dataframe[["Value"]])
  return(dataframe)
}

gradmatchlist <- a2ld(Gradmatcharray, 3) %>% lapply(FUN = convert_to_number)
envmatchlist <- a2ld(Envmatcharray, 3) %>% lapply(FUN = convert_to_number)

#Identify extant populations and sum them
extantfunc <- function(df){
  df2 <- df %>% mutate(Variable = "Extant", Value2 = case_when(is.na(Value) ~ 0, Value == 0~0, Value > 0 ~ 1)) %>% select(-Value) %>% rename(Value = Value2)
  return(df2)
  }
  


extantlist <- lapply(poplist, FUN = extantfunc)


#pivot everything so that we have differentials between each type of rescue and the no-rescue scenario
datapivot <- function(df) {
  data.frame(df) %>% pivot_wider(names_from = Rescue, values_from = Value) %>% mutate(DemographicDiff = Demographic-None, GradDiff = Grad - None, GradEnvDiff = GradEnv - None, MultipleDiff = Multiple - None)
}


extantlistrescue <- lapply(extantlist, FUN = datapivot)
poplistrescue <- lapply(poplist, FUN = datapivot)
gradlistrescue <- lapply(gradmatchlist, FUN = datapivot)
envlistrescue <- lapply(envmatchlist, FUN = datapivot)
gradvarlistrescue <- lapply(gradvarlist, FUN = datapivot)
envvarlistrescue <- lapply(envvarlist, FUN = datapivot)

#Recipient subsets
#pre-allocate
extantlistrescue_recip <- vector("list", 3600)
poplistrescue_recip <- vector("list", 3600)
gradlistrescue_recip <- vector("list", 3600)
envlistrescue_recip <- vector("list", 3600)
gradvarlistrescue_recip <- vector("list", 3600)
envvarlistrescue_recip <- vector("list", 3600)

#Recipient Subsets
#This is more complicated than the for loop below because there are different recipients in each rescue
#for (i in 1:3600){
#  poplistrescue_recip[[i]] <- semi_join(poplistrescue[[i]],DRlistlist[[i]])
#}

#The 5 sites that had the smallest population before rescue

#Now we have to summarize the rescue differentials within each of these three subsets


#get the column means/sum and variances then plot

sumdf <- function(df){
  colSums(df[,4:12], na.rm = TRUE)
}

meandf <- function(df){
  colMeans(df[,4:12], na.rm = TRUE)
}

extantlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue, FUN = sumdf, simplify = TRUE))))
poplistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue, FUN = meandf, simplify = TRUE))))
gradlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue, FUN = meandf, simplify = TRUE))))
envlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue, FUN = meandf, simplify = TRUE))))
gradvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue, FUN = meandf, simplify = TRUE))))
envvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue, FUN = meandf, simplify = TRUE)))) 

extantlistrescuecomb <-select(extantlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "Extant")
poplistrescuecomb <-select(poplistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "Pop.Size")
gradlistrescuecomb <-select(gradlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "Grad.Maladaptation")
envlistrescuecomb <-select(envlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "Env.Maladaptation")
gradvarlistrescuecomb <-select(gradvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "GradVar")
envvarlistrescuecomb <-select(envvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "EnvVar")

rescuecomb <- rbind(extantlistrescuecomb, poplistrescuecomb, gradlistrescuecomb, envlistrescuecomb, gradvarlistrescuecomb, envvarlistrescuecomb) %>% pivot_longer(cols = DemographicDiff:MultipleDiff, names_to = "Diff", values_to = "Value")

rescuecombplot <- rescuecomb %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")

#Analyses
summary(lm(DemographicDiff~EnvType*I(log10(Mig+0.000001))*Sel, data = extantlistrescuesum))


#Combine these into one 


extantplot <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

popplot <- poplistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#Extant counted NAs as 0s, this corrects that based on the population size data
extantplot[which(is.na(popplot), arr.ind = TRUE)]<-NA

gradplot <- gradlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envplot <- envlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

gradvarplot <- gradvarlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envvarplot <- envvarlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#further reduced
extantplotmig <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, MuMovement))

extantplotsel <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Sel, Omega2grad))

```

```{r tempplot}



difflabs <- c("Nearest Neighbor", "Gradient-Matched", "Gradient&Env-Matched", "Multi-Source")
names(difflabs) <- c("DemographicDiff", "GradDiff", "GradEnvDiff", "MultipleDiff")

smalltxtsize <- 8

#Fixed Environment

fexplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Extant"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Populations\nExtant", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Extant")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

fpsplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Pop.Size"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Population\nSize", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Pop.Size")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

fgmplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Grad.Maladaptation"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Gradient-\nPhenotype\nMaladaptation", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Grad.Maladaptation")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

femplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Env.Maladaptation"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Environment-\nPhenotype\nMaladaptation", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "Env.Maladaptation")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

fgvplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "GradVar"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Gradient\nPhenotypic\nVariance", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "GradVar")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

fevplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "EnvVar"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Environment\nPhenotypic\nVariance", limits = range(filter(rescuecombplot, ((EnvType == "Fixed")&(Variable == "EnvVar")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

fixedplot <- ggarrange(fexplot, fpsplot, fgmplot, femplot, fgvplot, fevplot, ncol = 1)
fixedplot2 <- annotate_figure(fixedplot, left = textGrob("Selection Strength (1/omega^2)", rot = 90, vjust = 1, gp = gpar(cex=1)), bottom = textGrob("Proportion Migrants", vjust= -0.25, gp = gpar(cex = 1)), top = textGrob("Fixed Environment", gp = gpar(cex=1)))
  
pdf(file = "./Outputs/V2 Figures/diffplot_fixed.pdf", height = 10, width = 7.5)
fixedplot2
dev.off()

#Variable Environment  

vexplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Extant"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Populations\nExtant", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Extant")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

vpsplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Pop.Size"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Population\nSize", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Pop.Size")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

vgmplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Grad.Maladaptation"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Gradient-\nPhenotype\nMaladaptation", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Grad.Maladaptation")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

vemplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Env.Maladaptation"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Environment-\nPhenotype\nMaladaptation", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "Env.Maladaptation")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

vgvplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "GradVar"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Gradient\nPhenotypic\nVariance", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "GradVar")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

vevplot <- ggplot(data = filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "EnvVar"))), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + facet_grid(.~Diff, labeller = labeller(Diff = difflabs)) + scale_fill_gradient2(name = "Environment\nPhenotypic\nVariance", limits = range(filter(rescuecombplot, ((EnvType == "Variable")&(Variable == "EnvVar")))$Value), low = "red", mid = "white", high = "blue", midpoint = 0) + scale_x_continuous(name = NULL, breaks = log10(c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1)), labels = c("0", "1e-05", "1e-04", "1e-03", "1e-02", "1e-01")) + scale_y_continuous(name = NULL, breaks = -1:-10, labels = c("1", "1/2", "1/3", "1/4", "1/5", "1/6", "1/7", "1/8", "1/9", "1/10")) + theme_classic() + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))

variableplot <- ggarrange(vexplot, vpsplot, vgmplot, vemplot, vgvplot, fevplot, ncol = 1)
variableplot2 <- annotate_figure(variableplot, left = textGrob("Selection Strength (1/omega^2)", rot = 90, vjust = 1, gp = gpar(cex=1)), bottom = textGrob("Proportion Migrants", vjust= -0.25, gp = gpar(cex = 1)), top = textGrob("Variable Environment", gp = gpar(cex=1))) + theme(axis.text.y = element_text(size = smalltxtsize), axis.text.x  = element_text(size = smalltxtsize, angle = 45, vjust = 1, hjust = 1))
  
pdf(file = "./Outputs/V2 Figures/diffplot_variable.pdf", height = 10, width = 7.5)
variableplot2
dev.off()


```

```{r singleplots}
#Extant
ggplot(data = extantplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Populations Extant") + theme_classic()

ggplot(data = extantplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Populations Extant") + theme_classic()

ggplot(data = extantplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Populations Extant") + theme_classic()

ggplot(data = extantplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Populations Extant") + theme_classic()

#Pop

ggplot(data = popplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Population Size") + theme_classic()

ggplot(data = popplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Population Size") + theme_classic()

ggplot(data = popplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Population Size") + theme_classic()

ggplot(data = popplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Population Size") + theme_classic()

#gradmatch

ggplot(data = gradplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotype\nMismatch Size") + theme_classic()

ggplot(data = gradplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotype\nMismatch") + theme_classic()

ggplot(data = gradplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotype\nMismatch") + theme_classic()

ggplot(data = gradplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotype\nMismatch") + theme_classic()

#envmatch

ggplot(data = envplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotype\nMismatch") + theme_classic()

ggplot(data = envplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotype\nMismatch") + theme_classic()

ggplot(data = envplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotype\nMismatch") + theme_classic()

ggplot(data = envplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotype\nMismatch") + theme_classic()

#gradvar
ggplot(data = gradvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotypic\nVariance") + theme_classic()

ggplot(data = gradvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotypic\nVariance") + theme_classic()

ggplot(data = gradvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotypic\nVariance") + theme_classic()

ggplot(data = gradvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Gradient\nPhenotypic\nVariance") + theme_classic()


#envvar
ggplot(data = envvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = DemographicDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotypic\nVariance") + theme_classic()

ggplot(data = envvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Envrionment\nPhenotypic\nVariance") + theme_classic()

ggplot(data = envvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = GradEnvDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotypic\nVariance") + theme_classic()

ggplot(data = envvarplot, aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = MultipleDiff_mean)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Environment\nPhenotypic\nVariance") + theme_classic()

```

```{r rescuecombplots}

#(data = filter(rescuecombplot, Variable == "Extant"), aes(x = log10(Mig+0.000001), y = -(1/Sel), fill = Value)) + geom_tile() + scale_fill_gradient2(low = "red", mid = "white", high = "blue", midpoint = 0) + facet_grid(~EnvType) + ggtitle("Populations Extant") + theme_classic()


```

```{r saverescuedata}

#save.image("RescueData.Rdata")

```



```
