---
title: "DataCleaning_Rescue"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

Process Remaining Rescue-Scenario Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(viridis)
library(ggpubr)
library(colorspace)
library(grid)
library(gdata)
library(str2str)
library(parallel)
library(beepr)

```


```{r loaddata}
load("loadedFullList.Rdata")
```

There are 3 types of comparisons worth making:
1. Comparing the average of all sites on the landscape between no rescue and rescue - did the effect percolate up to the whole metapopulation
2. Comparing the (5) demes with the smallest nonzero population size between no rescue and rescue - did the effect the most marginal demes in the metapopulation
3. Comparing the (5) demes that received supplementation between no rescue and rescue - did the target demes benefit? 

```{r functions}
#Find the data at time point 499, just before rescue occurs
prerescuedatasubset <- function(x){
  filter(x[[1]], Time == 499)
}

```

```{r cleanrescuedata}

#format grad and env match then pivot everything so that we have differentials between each type of rescue and the no-rescue scenario


convert_to_number <- function(dataframe){
  dataframe[["Value"]] <- as.numeric(dataframe[["Value"]])
  return(dataframe)
}

gradmatchlist <- a2ld(Gradmatcharray, 3) %>% lapply(FUN = convert_to_number)
envmatchlist <- a2ld(Envmatcharray, 3) %>% lapply(FUN = convert_to_number)



#pivot everything so that we have differentials between each type of rescue and the no-rescue scenario
datapivot <- function(df) {
  data.frame(df) %>% pivot_wider(names_from = Rescue, values_from = Value) %>% mutate(DemographicDiff = Demographic-None, GradDiff = Grad - None, GradEnvDiff = GradEnv - None, MultipleDiff = Multiple - None)
}


poplistrescue <- lapply(poplist, FUN = datapivot)
gradlistrescue <- lapply(gradmatchlist, FUN = datapivot)
envlistrescue <- lapply(envmatchlist, FUN = datapivot)
gradvarlistrescue <- lapply(gradvarlist, FUN = datapivot)
envvarlistrescue <- lapply(envvarlist, FUN = datapivot)

#Recipient subsets
#pre-allocate
poplistrescue_recip <- vector("list", 3600)
gradlistrescue_recip <- vector("list", 3600)
envlistrescue_recip <- vector("list", 3600)
gradvarlistrescue_recip <- vector("list", 3600)
envvarlistrescue_recip <- vector("list", 3600)

#Recipient Subsets
#This is more complicated than the for loop below because there are different recipients in each rescue
for (i in 1:3600){
  poplistrescue_recip[[i]] <- semi_join(poplistrescue[[i]],DRlistlist[[i]])
}

#The 5 sites that had the smallest population before rescue

#Now we have to summarize the rescue differentials within each of these three subsets


#get the column means and variances then plot

sumdf <- function(df){
  colMeans(df[,4:12], na.rm = TRUE)
}

poplistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue, FUN = sumdf, simplify = TRUE))))
gradlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue, FUN = sumdf, simplify = TRUE))))
envlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue, FUN = sumdf, simplify = TRUE))))
gradvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue, FUN = sumdf, simplify = TRUE))))
envvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue, FUN = sumdf, simplify = TRUE))))




```

```{r tempplot}
ggplot(data = poplistrescuesum, aes(x = -log10(Mig+0.000001), y = -Omega2grad, fill = DemographicDiff)) + geom_tile() + scale_fill_gradient2(low = 'red', mid = 'white', high = 'blue', midpoint = 0) + facet_grid(~EnvType) + ggtitle("Demographic Difference") + theme_classic()

ggplot(data = poplistrescuesum, aes(x = -log10(Mig+0.000001), y = -Omega2grad, fill = GradDiff)) + geom_tile() + scale_fill_gradient2(low = 'red', mid = 'white', high = 'blue', midpoint = 0) + facet_grid(~EnvType) + ggtitle("Grad Difference") + theme_classic()

ggplot(data = poplistrescuesum, aes(x = -log10(Mig+0.000001), y = -Omega2grad, fill = GradEnvDiff)) + geom_tile() + scale_fill_gradient2(low = 'red', mid = 'white', high = 'blue', midpoint = 0) + facet_grid(~EnvType) + ggtitle("Grad/Env Difference") + theme_classic()

ggplot(data = poplistrescuesum, aes(x = -log10(Mig+0.000001), y = -Omega2grad, fill = Multiple)) + geom_tile() + scale_fill_gradient2(low = 'red', mid = 'white', high = 'blue', midpoint = 0) + facet_grid(~EnvType) + ggtitle("Multiple Difference") + theme_classic()

###

```


```{r saverescuedata}

save.image("RescueData.Rdata")

```



```
