---
title: "DataCleaning_Rescue"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

Process Remaining Rescue-Scenario Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(viridis)
library(ggpubr)
library(colorspace)
library(grid)
library(gdata)
library(str2str)
library(parallel)
library(beepr)

```


```{r loaddata}
load("loadedFullList.Rdata")
```

There are 3 types of comparisons worth making:
1. Comparing the average of all sites on the landscape between no rescue and rescue - did the effect percolate up to the whole metapopulation
2. Comparing the (5) demes with the smallest nonzero population size between no rescue and rescue - did the effect the most marginal demes in the metapopulation
3. Comparing the (5) demes that received supplementation between no rescue and rescue - did the target demes benefit? 

```{r functions}
#Find the data at time point 499, just before rescue occurs
prerescuedatasubset <- function(x){
  filter(x[[1]], Time == 499)
}

```

```{r cleanrescuedata}

datapivot <- function(df) {
  data.frame(df) %>% pivot_wider(names_from = Rescue, values_from = Value)
}

dataarrayrescue <- lapply(datalist, FUN = datapivot)


```

```{r saverescuedata}

save.image("RescueData.Rdata")

```



```
