---
title: "DataCleaning_Rescue"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

Process Remaining Rescue-Scenario Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(viridis)
library(ggpubr)
library(colorspace)
library(grid)
library(gdata)
library(str2str)
library(parallel)
library(beepr)
library(rvg)
library(officer)
```


```{r loaddata}
#load("loadedFullListUpdated.Rdata")
#load("loadedMutationTest3List.Rdata")
#load("loaded_revision_List.Rdata")
load("loaded_omeg20List.Rdata")
```

There are 3 types of comparisons worth making:
1. Comparing the average of all sites on the landscape between no rescue and rescue - did the effect percolate up to the whole metapopulation
2. Comparing the (5) demes with the smallest nonzero population size between no rescue and rescue - did the effect the most marginal demes in the metapopulation
3. Comparing the (5) demes that received supplementation between no rescue and rescue - did the target demes benefit? 

So far this only implements #1 & #3

```{r functions}
#Find the data at time point 550, just before rescue occurs
prerescuedatasubset <- function(x){
  filter(x[[1]], Time == 550)
}
```


```{r cleanrescuedata}

#format grad and env match then pivot everything so that we have differentials between each type of rescue and the no-rescue scenario


convert_to_number <- function(dataframe){
  dataframe[["Value"]] <- as.numeric(dataframe[["Value"]])
  return(dataframe)
}

gradmatchlist <- a2ld(Gradmatcharray, 3) %>% lapply(FUN = convert_to_number)
envmatchlist <- a2ld(Envmatcharray, 3) %>% lapply(FUN = convert_to_number)

#Identify extant populations and sum them
extantfunc <- function(df){
  df2 <- df %>% mutate(Variable = "Extant", Value2 = case_when(is.na(Value) ~ 0, Value == 0~0, Value > 0 ~ 1)) %>% select(-Value) %>% rename(Value = Value2)
  return(df2)
  }
  


extantlist <- lapply(poplist, FUN = extantfunc)


extantfunc2 <- function(df){
  df2 <- df %>% mutate(Variable = "Extant", Value2 = case_when(is.na(Value) ~ NA, Value == 0 ~ 0, Value > 0 ~ 1)) %>% select(-Value) %>% rename(Value = Value2)
  return(df2)
}

extantlist2 <- lapply(poplist, FUN = extantfunc2)

#pivot everything so that we have differentials between each type of rescue and the no-rescue scenario
datapivot <- function(df) {
  data.frame(df) %>% pivot_wider(names_from = Rescue, values_from = Value) %>% mutate(DemographicDiff = Demographic-None, GradDiff = Grad - None, GradEnvDiff = GradEnv - None, PhenDiff = Phenotype - None, MultipleDiff = Multiple - None, GradAdjDiff = GradAdj - None, GradEnvAdjDiff = GradEnvAdj -  None)
}


extantlistrescue <- lapply(extantlist, FUN = datapivot)
extantlistrescue2 <- lapply(extantlist2, FUN = datapivot)
poplistrescue <- lapply(poplist, FUN = datapivot)
gradlistrescue <- lapply(gradmatchlist, FUN = datapivot)
envlistrescue <- lapply(envmatchlist, FUN = datapivot)
gradvarlistrescue <- lapply(gradvarlist, FUN = datapivot)
envvarlistrescue <- lapply(envvarlist, FUN = datapivot)



#Recipient Subsets
#This is more complicated than the for loop below because there are different recipients in each rescue
#for (i in 1:3600){
#  poplistrescue_recip[[i]] <- semi_join(poplistrescue[[i]],DRlistlist[[i]])
#}

#The 5 sites that had the smallest population before rescue

#Now we have to summarize the rescue differentials within each of these three subsets


#get the column means/sum and variances then plot

sumdf <- function(df){
  colSums(df[,4:18], na.rm = TRUE)
}

sumdf2 <- function(df){
  colSums(df[,4:18], na.rm = FALSE)
}

meandf <- function(df){
  colMeans(df[,4:18], na.rm = TRUE)
}

#9/7/2026 Here I change the meandf function so that it populations whose size is listed as NA are converted to 0. NAs come from when the whole metapopulation is extinct and 0s from when some populations are still extant, but it means we make apples to oranges comparisons later on.


meandfnona <- function(df){
  colSums(df[,4:18], na.rm = TRUE)/nrow(df)
  
}

extantlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue, FUN = sumdf, simplify = TRUE))))
extantlistrescuesum2 <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue2, FUN = sumdf2, simplify = TRUE))))
poplistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue, FUN = meandfnona, simplify = TRUE))))
gradlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue, FUN = meandf, simplify = TRUE))))
envlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue, FUN = meandf, simplify = TRUE))))
gradvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue, FUN = meandf, simplify = TRUE))))
envvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue, FUN = meandf, simplify = TRUE)))) 

extantlistrescuecomb <-select(extantlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Extant")
extantlistrescuecomb2 <-select(extantlistrescuesum2, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Extant")


poplistrescuecomb <-select(poplistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Pop.Size")
gradlistrescuecomb <-select(gradlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Grad.Maladaptation")
envlistrescuecomb <-select(envlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Env.Maladaptation")
gradvarlistrescuecomb <-select(gradvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, PhenDiff, GradEnvDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "GradVar")
envvarlistrescuecomb <-select(envvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, PhenDiff, GradEnvDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "EnvVar")

rescuecomb <- rbind(extantlistrescuecomb, poplistrescuecomb, gradlistrescuecomb, envlistrescuecomb, gradvarlistrescuecomb, envvarlistrescuecomb) %>% pivot_longer(cols = DemographicDiff:GradEnvAdjDiff, names_to = "Diff", values_to = "Value")

rescuecomb2 <- rbind(extantlistrescuecomb2, poplistrescuecomb, gradlistrescuecomb, envlistrescuecomb, gradvarlistrescuecomb, envvarlistrescuecomb) %>% pivot_longer(cols = DemographicDiff:GradEnvAdjDiff, names_to = "Diff", values_to = "Value")

rescuecombplot <- rescuecomb %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescuecombplot$Diff <- factor(rescuecombplot$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff", "GradAdjDiff", "GradEnvAdjDiff"))

rescuecombplot2 <- rescuecomb2 %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescuecombplot$Diff <- factor(rescuecombplot2$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff", "GradAdjDiff", "GradEnvAdjDiff"))


#Analyses
summary(lm(DemographicDiff~EnvType*I(log10(Mig+0.000001))*Sel, data = extantlistrescuesum))


#Combine these into one 


extantplot <- extantlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

extantplot2 <- extantlistrescuesum2 %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

popplot <- poplistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#Extant counted NAs as 0s, this corrects that based on the population size data
extantplot[which(is.na(popplot), arr.ind = TRUE)]<-NA

gradplot <- gradlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envplot <- envlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

gradvarplot <- gradvarlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envvarplot <- envvarlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#further reduced
extantplotmig <- extantlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, MuMovement))

extantplotsel <- extantlistrescuesum %>% summarize(across(DemographicDiff:GradEnvAdjDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Sel, Omega2grad))

```

```{r rescuedsitesonly}

recipients <- DRlistarray[,1,]


#Recipient subsets
#pre-allocate
extantlistrescue_recip <- vector("list", length(extantlistrescue))
extantlistrescue_recip2 <- vector("list", length(extantlistrescue2))
poplistrescue_recip <- vector("list", length(poplistrescue))
gradlistrescue_recip <- vector("list", length(gradlistrescue))
envlistrescue_recip <- vector("list", length(envlistrescue))
gradvarlistrescue_recip <- vector("list", length(gradvarlistrescue))
envvarlistrescue_recip <- vector("list", length(envvarlistrescue))



for (i in 1:length(extantlistrescue)){
extantlistrescue_recip[[i]] <- filter(extantlistrescue[[i]], Site %in% recipients[,i])
extantlistrescue_recip2[[i]] <- filter(extantlistrescue2[[i]], Site %in% recipients[,i])

#need to include the others here, and then make the same manipulations to this subset as we did to the whole
poplistrescue_recip[[i]] <- filter(poplistrescue[[i]], Site %in% recipients[,i])
gradlistrescue_recip[[i]] <- filter(gradlistrescue[[i]], Site %in% recipients[,i])
envlistrescue_recip[[i]] <- filter(envlistrescue[[i]], Site %in% recipients[,i])
gradvarlistrescue_recip[[i]] <- filter(gradvarlistrescue[[i]], Site %in% recipients[,i])
envvarlistrescue_recip[[i]] <- filter(envvarlistrescue[[i]], Site %in% recipients[,i])}


extantlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue_recip, FUN = sumdf, simplify = TRUE))))
extantlistrescue_recipsum2 <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue_recip2, FUN = sumdf2, simplify = TRUE))))

poplistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue_recip, FUN = meandfnona, simplify = TRUE))))
gradlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue_recip, FUN = meandf, simplify = TRUE))))
envlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue_recip, FUN = meandf, simplify = TRUE))))
gradvarlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue_recip, FUN = meandf, simplify = TRUE))))
envvarlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue_recip, FUN = meandf, simplify = TRUE)))) 

#Added on 9/9/2026 to remove any remaining 0s in 

extantlistrescue_recipcomb <-select(extantlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Extant")
extantlistrescue_recipcomb2 <-select(extantlistrescue_recipsum2, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Extant")

poplistrescue_recipcomb <-select(poplistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Pop.Size")
gradlistrescue_recipcomb <-select(gradlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Grad.Maladaptation")
envlistrescue_recipcomb <-select(envlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "Env.Maladaptation")
gradvarlistrescue_recipcomb <-select(gradvarlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "GradVar")
envvarlistrescue_recipcomb <-select(envvarlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff, GradAdjDiff, GradEnvAdjDiff) %>% mutate(Variable = "EnvVar")

rescue_recipcomb <- rbind(extantlistrescue_recipcomb, poplistrescue_recipcomb, gradlistrescue_recipcomb, envlistrescue_recipcomb, gradvarlistrescue_recipcomb, envvarlistrescue_recipcomb) %>% pivot_longer(cols = DemographicDiff:GradEnvAdjDiff, names_to = "Diff", values_to = "Value")

rescue_recipcomb2 <- rbind(extantlistrescue_recipcomb2, poplistrescue_recipcomb, gradlistrescue_recipcomb, envlistrescue_recipcomb, gradvarlistrescue_recipcomb, envvarlistrescue_recipcomb) %>% pivot_longer(cols = DemographicDiff:GradEnvAdjDiff, names_to = "Diff", values_to = "Value")

rescue_recipcombplot <- rescue_recipcomb %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescue_recipcombplot$Diff <- factor(rescue_recipcombplot$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff", "GradAdjDiff", "GradEnvAdjDiff"))

rescue_recipcombplot2 <- rescue_recipcomb2 %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescue_recipcombplot$Diff <- factor(rescue_recipcombplot2$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff", "GradAdjDiff", "GradEnvAdjDiff"))

#, ValSum = sum(Value, na.rm = TRUE), Value = ValSum/Num, 

```

```{r next}
#I'm interested in what the populations sizes of the recipient populations were at the time of donation - were they mostly 0s in some quadrants?


datalistpre <- mclapply(results_mclapplyall, FUN = prerescuedatasubset)
poplistpre <- lapply(datalistpre, FUN = filter, ((Variable == "Pop.Size")&(Rescue == "PreRescue")))


poplistprerecip <- vector("list", length(poplistpre))

for (j in 1:length(poplistprerecip)) {
  poplistprerecip[[j]] <- filter(poplistpre[[j]], Site %in% recipients[,j])
  poplistprerecip[[j]]$Extant <- 1*(poplistprerecip[[j]]$Value > 0)
  }


#9/7/2026 Here I started to change the popmeanfunc function so that it populations whose size is listed as NA are converted to 0.But since those only occur at this point if the whole metapopulation is extinct, and if the whole metapopulation is extinct before rescue then we're not testing rescue, it turns out to be unnecessary. popmeanfuncnona was the trial, but it turns out the results are identical. So I didn't have them affect anything.


popmeanfunc <- function(df){
  colMeans(df[,5:6], na.rm = TRUE)
}

popmeanfuncnona <- function(df){
  colSums(df[,5:6],na.rm=TRUE)/nrow(df)
}

popsumfunc <- function(df){
  colSums(df[,5:6], na.rm = TRUE)
}


poplistprerecipsum <- sapply(poplistprerecip, FUN = popsumfunc, simplify = TRUE)
poplistprerecipmean <-  sapply(poplistprerecip, FUN = popmeanfuncnona, simplify = TRUE)
poplistrescueprerecipsum <- cbind(Paramdfall, Extant = poplistprerecipsum[2,], Pop.Size = poplistprerecipmean[1,])

poplistrescueprerecipsumbyparameter <- poplistrescueprerecipsum %>% group_by(Mig,Sel, EnvType) %>% summarize(Pop.Size = mean(Pop.Size, na.rm = TRUE), Extant = mean(Extant, na.rm = TRUE), .groups = "keep")


for (j in 1:length(poplistpre)) {
  poplistpre[[j]]$Extant <- 1*(poplistpre[[j]]$Value > 0)
  }

poplistpresum <- sapply(poplistpre, FUN= popsumfunc, simplify=TRUE)
poplistpremean <-  sapply(poplistpre, FUN = popmeanfunc, simplify = TRUE)
poplistrescuepresum <- cbind(Paramdfall, Extant = poplistpresum[2,], Pop.Size = poplistpremean[1,])

poplistrescuepresumbyparameter <- poplistrescuepresum %>% group_by(Mig,Sel, EnvType) %>% summarize(Pop.Size = mean(Pop.Size, na.rm = TRUE), Extant = mean(Extant, na.rm = TRUE), .groups = "keep")

```

```{r savedata}
#save.image("RescueDataUpdated.Rdata")
#save.image("RescueData_Revision2.Rdata")
#save.image("RescueData_Revision3.Rdata")
save.image("RescueData_omega20.Rdata")
```

