---
title: "DataCleaning_Rescue"
author: "Ben Wasserman"
date: "`r Sys.Date()`"
output: html_document
---

Process Remaining Rescue-Scenario Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(viridis)
library(ggpubr)
library(colorspace)
library(grid)
library(gdata)
library(str2str)
library(parallel)
library(beepr)
library(rvg)
library(officer)
```


```{r loaddata}
#load("loadedFullListUpdated.Rdata")
load("loadedMutationTest3List.Rdata")
```

There are 3 types of comparisons worth making:
1. Comparing the average of all sites on the landscape between no rescue and rescue - did the effect percolate up to the whole metapopulation
2. Comparing the (5) demes with the smallest nonzero population size between no rescue and rescue - did the effect the most marginal demes in the metapopulation
3. Comparing the (5) demes that received supplementation between no rescue and rescue - did the target demes benefit? 

So far this only implements #1

```{r functions}
#Find the data at time point 499, just before rescue occurs
prerescuedatasubset <- function(x){
  filter(x[[1]], Time == 549)
}

```

```{r cleanrescuedata}

#format grad and env match then pivot everything so that we have differentials between each type of rescue and the no-rescue scenario


convert_to_number <- function(dataframe){
  dataframe[["Value"]] <- as.numeric(dataframe[["Value"]])
  return(dataframe)
}

gradmatchlist <- a2ld(Gradmatcharray, 3) %>% lapply(FUN = convert_to_number)
envmatchlist <- a2ld(Envmatcharray, 3) %>% lapply(FUN = convert_to_number)

#Identify extant populations and sum them
extantfunc <- function(df){
  df2 <- df %>% mutate(Variable = "Extant", Value2 = case_when(is.na(Value) ~ 0, Value == 0~0, Value > 0 ~ 1)) %>% select(-Value) %>% rename(Value = Value2)
  return(df2)
  }
  


extantlist <- lapply(poplist, FUN = extantfunc)


#pivot everything so that we have differentials between each type of rescue and the no-rescue scenario
datapivot <- function(df) {
  data.frame(df) %>% pivot_wider(names_from = Rescue, values_from = Value) %>% mutate(DemographicDiff = Demographic-None, GradDiff = Grad - None, GradEnvDiff = GradEnv - None, PhenDiff = Phenotype - None, MultipleDiff = Multiple - None)
}


extantlistrescue <- lapply(extantlist, FUN = datapivot)
poplistrescue <- lapply(poplist, FUN = datapivot)
gradlistrescue <- lapply(gradmatchlist, FUN = datapivot)
envlistrescue <- lapply(envmatchlist, FUN = datapivot)
gradvarlistrescue <- lapply(gradvarlist, FUN = datapivot)
envvarlistrescue <- lapply(envvarlist, FUN = datapivot)



#Recipient Subsets
#This is more complicated than the for loop below because there are different recipients in each rescue
#for (i in 1:3600){
#  poplistrescue_recip[[i]] <- semi_join(poplistrescue[[i]],DRlistlist[[i]])
#}

#The 5 sites that had the smallest population before rescue

#Now we have to summarize the rescue differentials within each of these three subsets


#get the column means/sum and variances then plot

sumdf <- function(df){
  colSums(df[,4:14], na.rm = TRUE)
}

meandf <- function(df){
  colMeans(df[,4:14], na.rm = TRUE)
}

extantlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue, FUN = sumdf, simplify = TRUE))))
poplistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue, FUN = meandf, simplify = TRUE))))
gradlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue, FUN = meandf, simplify = TRUE))))
envlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue, FUN = meandf, simplify = TRUE))))
gradvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue, FUN = meandf, simplify = TRUE))))
envvarlistrescuesum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue, FUN = meandf, simplify = TRUE)))) 

extantlistrescuecomb <-select(extantlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Extant")
poplistrescuecomb <-select(poplistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Pop.Size")
gradlistrescuecomb <-select(gradlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Grad.Maladaptation")
envlistrescuecomb <-select(envlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Env.Maladaptation")
gradvarlistrescuecomb <-select(gradvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, PhenDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "GradVar")
envvarlistrescuecomb <-select(envvarlistrescuesum, Sel, Mig, EnvType, DemographicDiff, GradDiff, PhenDiff, GradEnvDiff, MultipleDiff) %>% mutate(Variable = "EnvVar")

rescuecomb <- rbind(extantlistrescuecomb, poplistrescuecomb, gradlistrescuecomb, envlistrescuecomb, gradvarlistrescuecomb, envvarlistrescuecomb) %>% pivot_longer(cols = DemographicDiff:MultipleDiff, names_to = "Diff", values_to = "Value")

rescuecombplot <- rescuecomb %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescuecombplot$Diff <- factor(rescuecombplot$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff"))

#Analyses
summary(lm(DemographicDiff~EnvType*I(log10(Mig+0.000001))*Sel, data = extantlistrescuesum))


#Combine these into one 


extantplot <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

popplot <- poplistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#Extant counted NAs as 0s, this corrects that based on the population size data
extantplot[which(is.na(popplot), arr.ind = TRUE)]<-NA

gradplot <- gradlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envplot <- envlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

gradvarplot <- gradvarlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

envvarplot <- envvarlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, Sel, MuMovement, Omega2grad))

#further reduced
extantplotmig <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Mig, MuMovement))

extantplotsel <- extantlistrescuesum %>% summarize(across(DemographicDiff:MultipleDiff, .fns = list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))), .by = c(EnvType, Sel, Omega2grad))

```

```{r rescuedsitesonly}

recipients <- DRlistarray[,1,]


#Recipient subsets
#pre-allocate
extantlistrescue_recip <- vector("list", length(extantlistrescue))
poplistrescue_recip <- vector("list", length(poplistrescue))
gradlistrescue_recip <- vector("list", length(gradlistrescue))
envlistrescue_recip <- vector("list", length(envlistrescue))
gradvarlistrescue_recip <- vector("list", length(gradvarlistrescue))
envvarlistrescue_recip <- vector("list", length(envvarlistrescue))



for (i in 1:length(extantlistrescue)){
extantlistrescue_recip[[i]] <- filter(extantlistrescue[[i]], Site %in% recipients[,i])
#need to include the others here, and then make the same manipulations to this subset as we did to the whole
poplistrescue_recip[[i]] <- filter(poplistrescue[[i]], Site %in% recipients[,i])
gradlistrescue_recip[[i]] <- filter(gradlistrescue[[i]], Site %in% recipients[,i])
envlistrescue_recip[[i]] <- filter(envlistrescue[[i]], Site %in% recipients[,i])
gradvarlistrescue_recip[[i]] <- filter(gradvarlistrescue[[i]], Site %in% recipients[,i])
envvarlistrescue_recip[[i]] <- filter(envvarlistrescue[[i]], Site %in% recipients[,i])}



extantlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(extantlistrescue_recip, FUN = sumdf, simplify = TRUE))))
poplistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(poplistrescue_recip, FUN = meandf, simplify = TRUE))))
gradlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(gradlistrescue_recip, FUN = meandf, simplify = TRUE))))
envlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(envlistrescue_recip, FUN = meandf, simplify = TRUE))))
gradvarlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(gradvarlistrescue_recip, FUN = meandf, simplify = TRUE))))
envvarlistrescue_recipsum <- cbind(Paramdfall,data.frame(t(sapply(envvarlistrescue_recip, FUN = meandf, simplify = TRUE)))) 

extantlistrescue_recipcomb <-select(extantlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Extant")
poplistrescue_recipcomb <-select(poplistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Pop.Size")
gradlistrescue_recipcomb <-select(gradlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Grad.Maladaptation")
envlistrescue_recipcomb <-select(envlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "Env.Maladaptation")
gradvarlistrescue_recipcomb <-select(gradvarlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "GradVar")
envvarlistrescue_recipcomb <-select(envvarlistrescue_recipsum, Sel, Mig, EnvType, DemographicDiff, GradDiff, GradEnvDiff, PhenDiff, MultipleDiff) %>% mutate(Variable = "EnvVar")

rescue_recipcomb <- rbind(extantlistrescue_recipcomb, poplistrescue_recipcomb, gradlistrescue_recipcomb, envlistrescue_recipcomb, gradvarlistrescue_recipcomb, envvarlistrescue_recipcomb) %>% pivot_longer(cols = DemographicDiff:MultipleDiff, names_to = "Diff", values_to = "Value")

rescue_recipcombplot <- rescue_recipcomb %>% group_by(Sel, Mig, EnvType, Variable, Diff) %>% summarize(Value = mean(Value, na.rm = TRUE), .groups = "keep")
rescue_recipcombplot$Diff <- factor(rescue_recipcombplot$Diff, levels = c("DemographicDiff", "GradDiff", "GradEnvDiff", "PhenDiff", "MultipleDiff"))




```

```{r next}
#I'm interested in what the populations sizes of the recipient populations were at the time of donation - were they mostly 0s in some quadrants?


datalistpre <- mclapply(results_mclapplyall, FUN = prerescuedatasubset)
poplistpre <- lapply(datalistpre, FUN = filter, (Variable == "Pop.Size"))


poplistprerecip <- vector("list", length(poplistpre))

for (j in 1:length(poplistprerecip)) {
  poplistprerecip[[j]] <- filter(poplistpre[[j]], Site %in% recipients[,j])
  poplistprerecip[[j]]$Extant <- 1*(poplistprerecip[[j]]$Value > 0)
  }

popmeanfunc <- function(df){
  colMeans(df[,5:6], na.rm = TRUE)
}

popsumfunc <- function(df){
  colSums(df[,5:6], na.rm = TRUE)
}


poplistprerecipsum <- sapply(poplistprerecip, FUN = popsumfunc, simplify = TRUE)
poplistprerecipmean <-  sapply(poplistprerecip, FUN = popmeanfunc, simplify = TRUE)
poplistrescueprerecipsum <- cbind(Paramdfall, Extant = poplistprerecipsum[2,], Pop.Size = poplistprerecipmean[1,])

poplistrescueprerecipsumbyparameter <- poplistrescueprerecipsum %>% group_by(Mig,Sel, EnvType) %>% summarize(Pop.Size = mean(Pop.Size, na.rm = TRUE), Extant = mean(Extant, na.rm = TRUE), .groups = "keep")


```

```{r savedata}
#save.image("RescueDataUpdated.Rdata")
save.image("RescueDataMutationTest3.Rdata")
```

